---
title: "README"
output: github_document
---

# FP

## Overview

`FP` is a collection of my personal functions that I use in my workflow.
The goal is to make my workflow easier by either creating functions to
address simple tasks or build on existing packages to mold the functions
to my personal needs. “Stolen” ideas from here and there are referenced.

## Installation

All `FP` functions are on the same script. Once loaded, all functions will 
be available on `Global Environment`. To load the functions you can
source the script as follows:

```{r eval=FALSE}
source("https://raw.githubusercontent.com/fbparreira/FP/main/code.R")
```

## Functions

| **Name** | **Description** |
|:--:|:---:|
|`here()`|Sets the `wd` to the local path where the script is.|
|`column_clean()`|Cleans the `.` in the column's names. An issue where imported `.xlsx` files with spaces in columns have.|
|`readxlsx_allsheets()`|Reads all sheets in a `.xlsx` to a list.|
|`emptyxlsx()`|Creates an empty `.xlsx` file.|
|`writexlsx()`|Writes an `.xlsx` file.|
|`view_in_excel()`|Open a `df` directly in Excel, creating a temporary file. Alternative to the base `View()`.|
|`textplot()`|Plots text as a base `plot()`.|












## `here()`

### Description

When you are working on a script not within an `R project`, instead of using `setwd()` 
to manually paste the path, just run `here()`.

### Usage

```{r eval=FALSE}
here()
```
















## `column_clean()`

### Description

When importing `.xlsx` files using `openxlsx::read.xlsx` (my preferred package for dealing with `.xlsx` files) to a `df`, the white spaces in the column names are translated to `.`. The `column_clean` function 
restores the white spaces from those `.`.

### Usage

```{r eval=FALSE}
column_clean(df)
```

### Arguments

- `df` A Dataframe object.















## `readxlsx_allsheets()`

### Description

The `readxlsx_allsheets()` function imports all sheets of an `.xlsx` file to a list.

### Usage

```{r eval=FALSE}
readxlsx_allsheets(excel_file)
```

### Arguments

- `excel_file` Path to the `.xlsx` file.

### Example

```{r eval=FALSE}
# Import all sheets from `file.xlsx` to a list (`list_of_file_sheets`).
list_of_file_sheets <- 
  readxlsx_allsheets(excel_file = "path/to/file.xlsx")

# Assign the sheet named `sheet_name` to a `df`
df <- 
  list_of_file_sheets[["sheet_name"]]
```

### References

Idea stolen from this [post](https://stackoverflow.com/questions/12945687/read-all-worksheets-in-an-excel-workbook-into-an-r-list-with-data-frames)






















## `emptyxlsx()`

### Description

The `emptyxlsx()` function creates an empty `.xlsx` file. To me, this is particularly handy when running `for()` loops where I want each iteration to write in a different sheet of the same file.

### Usage

```{r eval=FALSE}
emptyxlsx(excel_file,
          overwrite = TRUE)
```

### Arguments

- `excel_file` Path to the `.xlsx` file.

- `overwrite` If `TRUE` (default), it overwrites an existing file.


















## `writexlsx()`

### Description

The `writexlsx()` function simplifies, to me, the use of the `openxlsx::` package to write `.xlsx` files. The `openxlsx::` package is my preferred package to deal with `.xlsx` files due to its versatility. However, its versatility comes at a tedious cost due to the way it uses the `workbooks`.I picked up the styles and functions I use the most on `openxlsx::` and combined them in the function `writexlsx()`.

### Usage

```{r eval=FALSE}
writexlsx(df,
          excel_file, 
          sheet_name = FALSE, 
          append_sheet = FALSE,
          filter = FALSE,
          alt_shading = FALSE,
          alt_shading_var,
          col_width_auto = FALSE,
          freeze_first_row = FALSE,
          bottom_border = FALSE,
          bottom_border_var)
```


### Arguments

- `df` Dataframe object.

- `excel_file` Path to write file.

- `sheet_name` Name for the Excel sheet. If empty/`FALSE` (default), it goes for Excel default.

- `append_sheet` If `FALSE` (default), overwrites an existing file. If `TRUE`, adds a new sheet to the existing file. A sheet_name is required in this case.

- `filter` (default = `FALSE`) If `TRUE`, applies a filter to the first row.

- `alt_shading` (default = `FALSE`) If `TRUE`, applies alternative fill color (grey and white) base on a variable (`alt_shading_var`).

- `alt_shading_var` A variable within the `df` to apply the `alt_shading`.

- `col_width_auto` (default = `FALSE`) If `TRUE`, automatically adjusts the column widths according to content.

- `freeze_first_row` (default = `FALSE`) If `TRUE`, freezes the first row.

- `bottom_border` (default = `FALSE`) If `TRUE`, applies a bottom border based on a variable (`bottom_border_var`).

- `bottom_border_var` A variable within the `df` to apply the `bottom_border`.

### References:

Idea stolen from [MarcioFCMartins](https://github.com/MarcioFCMartins/MMartins/blob/master/R/df_to_xlsx.R)




















## `view_in_excel()`

### Description

The function `view_in_excel()` allows to open a `df` directly in Excel. This is an alternative to the basic `View()` function, giving more flexibility when visually inspecting a `df`. It provides the path to the temporary file created. **It is dependent on** `writexlsx()`.

### Usage

```{r eval=FALSE}
view_in_excel(df, 
              filter = T,
              alt_shading = FALSE,
              alt_shading_var,
              col_width_auto = TRUE,
              freeze_first_row = TRUE,
              bottom_border = FALSE,
              bottom_border_var)
```


### Arguments

- `df` Dataframe object.

- `filter` If `TRUE` (default), applies a filter to the first row.

- `alt_shading` (default = `FALSE`) If `TRUE`, applies alternative fill color (grey and white) base on a variable (`alt_shading_var`).

- `alt_shading_var` A variable within the `df` to apply the `alt_shading`.

- `col_width_auto` If `TRUE` (default), automatically adjusts the column widths according to content.

- `freeze_first_row` If `TRUE` (default), freezes the first row.

- `bottom_border` (default = `FALSE`) If `TRUE`, applies a bottom border based on a variable (`bottom_border_var`).

- `bottom_border_var` A variable within the `df` to apply the `bottom_border`.

### References

Idea stolen from this [post](https://stackoverflow.com/questions/12164897/quickly-view-an-r-data-frame-vector-or-data-table-in-excel)





















## `textplot()`

### Description

The `textplot()` function plots text as a base `plot()`

### Usage

```{r eval=FALSE}
textplot(text, 
         size)
```

### Arguments 

- `text` Text to be plotted

- `Size` Size of the text