---
title: "README"
output: github_document
---


```{r eval=FALSE, include=FALSE}
# .RMD file to edit the README.MD file.

#render this .RMD to the .MD
library(rmarkdown)

render("README.Rmd", output_format = "md_document")
```



# FP

## Overview

`FP` is a collection of my personal functions that I use in my workflow.
The goal is to make my workflow easier by either creating functions to
address simple tasks or build on existing packages to mold the functions
to my personal needs. “Stolen” ideas from here and there are referenced.

## Installation

All `FP` functions are on the same script. Once loaded, all functions will 
be available on `Global Environment`. To load the functions you can
source the script as follows:

```{r eval=FALSE}
source("https://raw.githubusercontent.com/fbparreira/FP/main/code.R")
```

## Functions

| **Name** | **Description** |
|:--:|:---:|
|`here()`|Sets the `wd` to the local path where the script is.|
|`column_clean()`|Cleans the `.` in the column's names. An issue where imported `.xlsx` files with spaces in columns have.|
|`readxlsx_allsheets()`|Reads all sheets in a `.xlsx` to a list.|
|`emptyxlsx()`|Creates an empty `.xlsx` file.|
|`writexlsx()`|Writes an `.xlsx` file.|
|`view_in_excel()`|Open a `df` directly in Excel, creating a temporary file. Alternative to the base `View()`.|
|`textplot()`|Plots text as a base `plot()`.|

## `here()`

### Description

When you are working on a script not within an `R project`, instead of using `setwd()` 
to manually paste the path, just run `here()`.

### Usage

```{r eval=FALSE}
here()
```

## `column_clean()`

### Description

When importing `.xlsx` files using `openxlsx::read.xlsx` (my preferred package for dealing with `.xlsx` files) to a `df`, the white spaces in the column names are translated to `.`. The `column_clean` function 
replaces those `.` by `" "`.

### Usage

```{r eval=FALSE}
column_clean(df)
```

### Arguments

- `df` A Dataframe object.
